The importance of measurement uncertainty in ecological management

### 2017-09-29 manuscripts/manuscript.Rmd
WIP

@Clark1987 was among the first attempts to resolve Reed's Paradox. @Clark1987 (quite correctly, as we will see), identified the crux of Reed's Paradox as the absence of measurement uncertainty:

@@

Unfortunately, @Clark1987 was unable to solve the resulting problem exactly, but had to adopt an almost equally troublesome assumption:

@@

>>>>

@Clark1986 was among the first attempts to resolve Reed's Paradox. @Clark1986 (quite correctly, as we will see), identified the crux of Reed's Paradox as the absence of measurement uncertainty:

@@

Unfortunately, @Clark1986 was unable to solve the resulting problem exactly, but had to adopt an almost equally troublesome assumption:

@@

## POMDPs: An optimal treatment of measurement uncertainty

As discussed above, absent the short-cut provided by Reed's theorems, solving for the optimal management policy in a stochastically fluctuating population involves a Markov Decision Process (MDP), commonly referred to in ecological literature by its solution method, Stochastic Dynamic Programming (SDP). Once measurement uncertainty is introduced, the problem becomes a Partially Observed Markov Decision Process (POMDP, not be confused with a partially observed or hidden Markov model, HMM, in which no decision process is involved).  As in the case of MDP, such problems can be solved by existing and well-studied algorithms. While not unknown to the conservation literature [@Williams2009], algorithms for POMDP have historically scaled quite poorly, and their application has been restricted to contexts with only a handful of possible states and actions [e.g. @Chades, @Fackler, ....].  POMDP algorithms remain a very active area in artificial intellegence, and by adapting recent algorithmic developments [@Kurtwani] from that field we are able to find solutions for the considerably more complex problems such as the case of fisheries managment, which requires on the order of 100 states and actions to provide sufficient numerical resolution.  <!--  -->

We will not summarize all of the technical details here which are already well-developed in the existing POMDP literature, but rather we focus on providing the essential intuition behind decisions under a POMDP as compared to a perfectly observed system.  For readers interested in exploring or applying these methods in more depth, we have developed a preliminary R package which can be used to replicate any of the results presented here [@Rsarsop].

## Results

Figure 1 shows the results of simulation

-------------
